Interval Probability for Fuzzy Quantum Theories

### 2016-06-04 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} starting to update my last comment...

%%%%%
\subsection{Quantum Interval-valued Probabilities Measures}
\yutsung{Vourdas' first paper~\cite{Vourdas2014} is interesting
and highly readable until section IV. However, I don't understand
since the second sentence in section IV:
\begin{itemize}
\item If $\mathfrak{d}\left(H_{1},H_{2}\middle|\rho\right)\ge0$, then $p\left(H_{1}\middle|\rho\right)$
and $p\left(H_{2}\middle|\rho\right)$ are lower probabilities. Also,
according to Eq. (22), in this case $\mathfrak{d}\left(H_{1}^{\perp},H_{2}^{\perp}\middle|\rho\right)\le0$,
and therefore the $p\left(H_{1}^{\perp}\middle|\rho\right)$ and $p\left(H_{2}^{\perp}\middle|\rho\right)$
are upper probabilities.
\end{itemize}
I assume Vourdas means that $p\left(H_{1}\middle|\rho\right)$ and
$p\left(H_{1}^{\perp}\middle|\rho\right)$ are the lower and upper
probability respectively for measuring subspace~$H_{1}$ on the system~$\rho$.
Consider the simplest example the subspace $H_{1}$ is the zero space
$\mathcal{O}$ which commutes with every other subspaces, so $\mathfrak{d}\left(\mathcal{O},H_{2}\middle|\rho\right)=0$.
Then, for measuring $\mathcal{O}$ on $\rho$, the lower and upper
probabilities are $p\left(\mathcal{O}\middle|\rho\right)=0$ and $p\left(\mathcal{O}^{\perp}\middle|\rho\right)=p\left(\mathcal{I}\middle|\rho\right)=1$,
respectively. The lower probability is $0$ makes sense, but I don't
understand why the upper probability is $1$. Because both the lower
and upper probabilities of the empty set are $0$ in classical Dempster-Shafer
theory.

>>>>

%%%%%
\subsection{Quantum Interval-valued Probabilities Measures}

\yutsung{Vourdas' first paper~\cite{Vourdas2014} is interesting
and highly readable until section IV. In particular, the comparison
between the Kolmogorov's
\[
\delta\left(A,B\right)=q\left(A\vee B\right)-q\left(A\right)-q\left(B\right)+q\left(A\wedge B\right)
\]
where $A$ and $B$ are events, and $q\left(A\right)$ is the probability
of $A$; and its quantum counterpart 
\[
\mathfrak{D}\left(H_{1},H_{2}\right)=\mathfrak{P}\left(H_{1}\vee H_{2}\right)-\mathfrak{P}\left(H_{1}\right)-\mathfrak{P}\left(H_{2}\right)+\mathfrak{P}\left(H_{1}\wedge H_{2}\right)
\]

However, his section VI is confusing. For example, the second sentence
in section IV: 
\begin{itemize}
\item If $\mathfrak{d}\left(H_{1},H_{2}\middle|\rho\right)\ge0$, then $p\left(H_{1}\middle|\rho\right)$
and $p\left(H_{2}\middle|\rho\right)$ are lower probabilities. Also,
according to Eq. (22), in this case $\mathfrak{d}\left(H_{1}^{\perp},H_{2}^{\perp}\middle|\rho\right)\le0$,
and therefore the $p\left(H_{1}^{\perp}\middle|\rho\right)$ and $p\left(H_{2}^{\perp}\middle|\rho\right)$
are upper probabilities.
\end{itemize}
I assume Vourdas means that $p\left(H_{1}\middle|\rho\right)$ and
$p\left(H_{1}^{\perp}\middle|\rho\right)$ are the lower and upper
probability respectively for measuring subspace~$H_{1}$ on the system~$\rho$.
Consider the simplest example the subspace $H_{1}$ is the zero space
$\mathcal{O}$ which commutes with every other subspaces, so $\mathfrak{d}\left(\mathcal{O},H_{2}\middle|\rho\right)=0$.
Then, for measuring $\mathcal{O}$ on $\rho$, the lower and upper
probabilities are $p\left(\mathcal{O}\middle|\rho\right)=0$ and $p\left(\mathcal{O}^{\perp}\middle|\rho\right)=p\left(\mathcal{I}\middle|\rho\right)=1$,
respectively. The lower probability is $0$ makes sense, but I don't
understand why the upper probability is $1$. Because both the lower
and upper probabilities of the empty set are $0$ in classical Dempster-Shafer
theory.
